### 2019-04-03 _publications/jors/paper.tex
Fix spellings

%% Journal of Open Research Software Latex template -- Created By Stephen Bonner and John Brennan, Durham Universtiy, UK.

@@

Scientific communities struggle with the challenge of effectively and
efficiently sharing content and data. An online portal provides a
valuable space for scientific communities to discuss challenges and
collate scientific results. Examples of such portals include the
Micromagenetic Modeling Group ($\mu$MAG~\cite{mumag}), the Iteratomic
Potentials Repository (IPR~\cite{ipr1, ipr2}) and on a larger scale
the NIH Genetic Sequence Database (GenBank~\cite{genbank}). In this
work, we present a description of a generic web portal that leverages
existing online services to provide a framework that may be adopted by
other small scientific communities. The first deployment of the PFHub
framework supports phase-field practitioners and code developers
participating in an effort to improve quality assurance for
phase-field codes.

>>>>

%% Journal of Open Research Software Latex template -- Created By Stephen Bonner and John Brennan, Durham University, UK.

@@

Scientific communities struggle with the challenge of effectively and
efficiently sharing content and data. An online portal provides a
valuable space for scientific communities to discuss challenges and
collate scientific results. Examples of such portals include the
Micromagnetic Modeling Group ($\mu$MAG~\cite{mumag}), the Interatomic
Potentials Repository (IPR~\cite{ipr1, ipr2}) and on a larger scale
the NIH Genetic Sequence Database (GenBank~\cite{genbank}). In this
work, we present a description of a generic web portal that leverages
existing online services to provide a framework that may be adopted by
other small scientific communities. The first deployment of the PFHub
framework supports phase-field practitioners and code developers
participating in an effort to improve quality assurance for
phase-field codes.
